### 2021-10-14 documentos/vector_space.tex
Well, it's doing something.

\subsection{A vector space of channels} % {{{
% \begin{itemize} % {{{ Cosas por escribir aca
% \item Canales PCE como espacios vectoriales \todo{Francois escribe}
% \item Regla de $2^k$
% \item Tamaño de las diferentes clases que borran un numero fijo de componentes
% y tambien nota de qeu son igual entre complementarios: computo del numero de
% bases dada una dimension de subespacios vectoriales, aqui entra la formula del
% binomial-q. \todo{Esperemos que evolucione mas el articulo y luego vemos que ponemos}
% \item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
% \item \ddnote{Agrego esto:} A final remarks of the derivation as a tool.
% Concepts might be complicated, but the tool gives some simple rules to the
% reader: \textit{tell me what components you want to keep, and the (vector)
% summation rules will give you the rest of components to make the target
% operation a CPTP one.}
% \end{itemize} % }}}
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vtau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, so 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
% \san \lambda =2^N \tau
\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. 
\cpnote{resaltar aca la importancia de esa ecuacion, y que se aplica
para cualquier canal diagonal de Pauli}
Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:2N} from 
% $\sum_{\vec\beta}p_{\vec\beta}=1$ (which follows from \cpnote{ver constante de 
% normalizacion chido y ver el motivo}), and 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$ 
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}.

% 
% This follows from (\ref{eq:6}) as
% well as the fact that, due 
% to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.

Condition (\ref{eq:11}) therefore connects three multi-indices, $\vec\alpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection. \cpnote{I think that this paragraph can go. }

Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
as
\begin{equation}
\san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
= 
\san_{\valpha\vbeta} 
, \quad
\forall \vec\beta\in\Phi(\vec\alpha),
\label{eq:12}
\end{equation}
which can be further decomposed in 
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
  \ldots
%   \cdot\ldots\cdot 
\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}
  \ldots
% \cdot\ldots\cdot
 \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
% Moreover, since 
% 
% 
% 
% Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% \label{eq:12}
% \end{equation}
% This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
% (\ref{eq:12}) may be rewritten as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
% \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
% \label{eq:13}
% \end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index\cpnote{francois, recuerdo 
que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
proque se tiene que cumplir para los indices individulaes}. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. One can verify, by working out the different cases, 
that \eref{eq:14} equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where the $\oplus{}$ denotes the operation of the Kein group; see Figure
\ref{tab:1} for a detailed description. 
% \cpnote{Quiza poner una relacion como $\tau_{\vgamma}=\tau_{\valpha\oplus{}\vgamma}$}

\par
% \cpnote{by direct calculation I can verify 
% that its true, but I see it as a coincidence. Is they ere a say to know
% that \eref{eq:14} will lead to a sum?}
% }}}

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$. 
We can indeed restate \eref{eq:oplus}, an say that for valid quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.

@@

From this readily follows an amusing property: the set of all multi-indices
$\vec\gamma$ for which $\tau_{\vec\gamma}=1$, is closed under binary
vector addition, in other words, it forms a vector subspace of the set
of all multi-indices.
A moment's consideration will further show that the above reasoning can be
inverted, that is, that if we set all $\tau_{\vec\gamma}$ equal to one
whenever the $\vec\gamma$ belong to a given vector subspace of the set of
all indices, then the vector $\vec\tau$ indeed has an image which is a vector
with only positive components. 
In other words, there is a one to one correspondence between 
a valid quantum channel, and a vector subspace of the aforementioned space. 
\cpnote{Aca quizá que Jose Alfredo ponga un ejemplo de una 
figura en la que se tenga algo que es un canal y algo que no es  un canal. 
Quizá también se puede mencionar qeu el subespacio mas chico es el canal totalmente 
depolarizante y el subespacio mas grande es la identidad}

% Indeed, let $\overline\alpha$ and $\overline\gamma$
% belong to that set. Then if 
% \begin{equation}
% \overline{\gamma^\prime}=\overline\alpha+\overline\gamma
% \label{eq:14b}
% \end{equation}
% then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
% and thus equal to one.

So we may now proceed to generate all solutions: we start out from the solution
having $\tau_{\vec0}=1$, with everything else $0$. We may then successively
switch $\tau$'s to $1$ for various values of $\valpha$, taking care
immediately to set equal to one the components of $\tau$ that correspond to values
of $\vbeta$ generated by the previously switched values of $\valpha$ via the
operation $\oplus$. Doing so, in an ordered way allows one to general 
all valid quantum channels with given preserved components, without the need
of exploring the exponentially large space of PCE. 
% (\ref{eq:11}).

% Procesado pero No lo entiendo/no lo quiero poner {{{

@@

%
%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$,
%nor to any site that is automatically equal to $\tau_{\alp1}$. Set
%$\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
%since the two are equal because of (\ref{eq:18}). By the same reasoning that
%led to (\ref{eq:18}), we now find that 
%\begin{equation}
%\tau_{\vec\gamma} = \tau_{\alp1\oplus{}\vec\gamma}
%     =\tau_{\alp2\oplus{}\vec\gamma}
%     =\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
%\label{eq:19}
%\end{equation}
%Thus we find that the $\tau$'s are now constant over domains of $4$, as
%opposed to $2$ previously, when only one
%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$.
%Further, it follows from the group property of $\oplus$ that the different
%domains are {\em disjoint}. The 3 multi-indices associated to a given
%$\vec\gamma$ are never associated to any other $\vec{\gamma^\prime}$. 
%
%After adding $\alp1$, we have at least 2 sites equal to 1, after adding
%$\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$.  Clearly, at
%each addition, the total number doubles. This shows the $2^k$ rule. 
%
%How far can this process go? Well, the total number of multi-indices is $4^N$,
%so this can go on until $2\cdot4^{N-1}$ sites are occupied, in other words, we
%may double $2N-1$ times.
%
%Now to show that the maximal solutions are generators, that is, that all
%solutions can be expressed as intersections of maximal solutions, that is,
%solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by
%the successive adjunction of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to
%the group property, the final solution generated does not depend on the order
%of the $\alp{k}$. 
%
%Now let us consider a solution with half the number of elements of a maximal
%solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$.  At this
%stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and
%there are a total of $4^{N-1}$ 1's.  There are thus 2 inequivalent remaining
%domains where I could put the final $\alp{2N-1}$. These 2 different choices
%yield disjoint maximal solutions, the intersection of which yields the
%solution with half the number of elements of the maximal solution.  Every
%solution one step away from maximal can thus be expressed (uniquely) as the
%intersection of 2 maximal solutions. 
%
%Arguing inductively backwards, the same result can be shown for arbitrary
%solutions. We therefore have shown both the $2^k$ rule and the fact that all
%solutions are expressible uniquely as intersections of maximal solutions.

The dimension of the vector space $V$ of all multi-indices is $2N$, and we have
seen earlier that
\begin{equation}
W=\left\{
\vec\alpha:\vec\alpha\in V, \tau_{\vec\alpha}=1
\right\}
\label{eq:19}
\end{equation}
is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that $W$ has $2^K$ elements. In other words,
a vector $\vec\tau$ with the property discussed above can only have $2^K$ elements equal to 1, for a given integer $K$.

By standard theorems of linear algebra, any subspace $W$ can be extended to a maximal (non-trivial) subspace of dimension
$2N-1$ by adjoining appropriate additional basis elements. This can clearly be done in different ways. We therefore arrive to
the set of maximal extensions of $W$. Clearly, the intersection of all the elements of this set reduces to $W$ itself, leading to
the result that all PCE's can be obtained as intersections of maximal PCE's.

\ddnote{Agrego esto:} A final remarks of the derivation as a tool. Concepts might be complicated, but the tool gives some simple rules to the reader: \textit{tell me what components you want to keep, and the (vector) summation rules will give you the rest of components to make the target operation a CPTP one.}

>>>>

\subsection{A vector space of channels} % {{{
\cpnote{Quiza falta lo de las clases de equivalencias}\par
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vtau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, so 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
% \san \lambda =2^N \tau
\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. 
This is a remarkable equation, as it provides a method to diagonalize any diagonal 
Pauli channel, as in \eref{eq:definition:Pauli}.

Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:2N} from 
% $\sum_{\vec\beta}p_{\vec\beta}=1$ (which follows from \cpnote{ver constante de 
% normalizacion chido y ver el motivo}), and 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$ 
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection.

Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
as
\begin{equation}
\san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
= 
\san_{\valpha\vbeta} 
, \quad
\forall \vec\beta\in\Phi(\vec\alpha),
\label{eq:12}
\end{equation}
which can be further decomposed in 
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
  \ldots
%   \cdot\ldots\cdot 
\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}
  \ldots
% \cdot\ldots\cdot
 \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
% Moreover, since 
% 
% 
% 
% Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% \label{eq:12}
% \end{equation}
% This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
% (\ref{eq:12}) may be rewritten as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
% \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
% \label{eq:13}
% \end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index\cpnote{francois, recuerdo 
que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
proque se tiene que cumplir para los indices individulaes}. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. One can verify, by working out the different cases, 
that \eref{eq:14} equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where the $\oplus{}$ denotes the operation of the Kein group; see Figure
\ref{tab:1} for a detailed description. 
% \cpnote{Quiza poner una relacion como $\tau_{\vgamma}=\tau_{\valpha\oplus{}\vgamma}$}
\par
% \cpnote{by direct calculation I can verify 
% that its true, but I see it as a coincidence. Is they ere a say to know
% that \eref{eq:14} will lead to a sum?}
% }}}
% Espacio vectorial {{{

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$
\footnote{
We can further \cpnote{desmechar} the vector space, by identifying each index
$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
such that to each multindex  $\valpha$ there corresponds a binary string of 
length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
each of the $2N$ components. 
\cpnote{maybe its not necesary}
}. 
We can indeed restate \eref{eq:oplus}, an say that for valid quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
% \cpnote{Creo que aca podemos referenciar la figura 2c y mostrar como
% funcionaria que no es cerrada bajo la suma}
For example, in \fref{fig:two:qubit:examples}(c) the indices that 
correspond to preserved components are 
$\valpha^{(0)} = (0,0)$, 
$\valpha^{(1)} = (0,2)$, 
$\valpha^{(2)} = (1,0)$, 
$\valpha^{(3)} = (2,2)$, and
$\valpha^{(4)} = (3,2)$. However, 
$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preseverd and thus this 
diagram does not correspond to a quantum channel.  From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.

@@

From this readily follows an amusing property: the set of all multi-indices
$\vec\gamma$ for which $\tau_{\vec\gamma}=1$, is closed under binary
vector addition, in other words, it forms a vector subspace of the set
of all multi-indices.
A moment's consideration will further show that the above reasoning can be
inverted, that is, that if we set all $\tau_{\vec\gamma}$ equal to one
whenever the $\vec\gamma$ belong to a given vector subspace of the set of
all indices, then the vector $\vec\tau$ indeed has an image which is a vector
with only positive components. 
In other words, there is a one to one correspondence between 
a valid quantum channel, and a vector subspace of the aforementioned space. 
\cpnote{Aca quizá que Jose Alfredo ponga un ejemplo de una 
figura en la que se tenga algo que es un canal y algo que no es  un canal. 
Quizá también se puede mencionar qeu el subespacio mas chico es el canal totalmente 
depolarizante y el subespacio mas grande es la identidad} \par
% Generacion de soluciones {{{
So we may now proceed to generate all solutions: we start out from the solution
having $\tau_{\vec0}=1$, with everything else $0$. We may then successively
switch $\tau$'s to $1$ for various values of $\valpha$, taking care
immediately to set equal to one the components of $\tau$ that correspond to values
of $\vbeta$ generated by the previously switched values of $\valpha$ via the
operation $\oplus$. Doing so, in an ordered way, allows one to general 
all valid quantum channels with a given set of preserved components, without the need
of exploring the exponentially large space of PCE.  \par 

@@

\begin{figure} % {{{
\begin{center}
% Del dcumento francois.pdf pg 8 agarramos:
% e11, e4 y E7
\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
\pgfmathsetmacro{\unitstep}{5.2}
\begin{scope}[shift={(1*\unitstep,0)}] % Depolirizng channel {{{
\node at (-0.5,0.5) {(a)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Interseccion {{{
\node at (-0.5,0.5) {(b)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(3*\unitstep,0)}] % E4 {{{
\node at (-0.5,0.5) {(c)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(1,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(1*\unitstep,-\unitstep)}] % E7 {{{
\node at (-0.5,0.5) {(d)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(1,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,-\unitstep)}] % E11 {{{
\node at (-0.5,0.5) {(e)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(1,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(3*\unitstep,-\unitstep)}] % Identity channel {{{
\node at (-0.5,0.5) {(f)} ;
